SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-04 docs/questioning.tex
more on the intro and abstract

  We then categorize and analyze the various defense mechanisms that
  have been developed. Our analysis is based on dimensions such as
  accuracy, performance, deployment and security. Especially notable
  for a key category is accuracy, as our findings show that there are
  many defense mechanisms that are tested in a poor manner.

@@

@@

There is already a survey on mitigating
software vulnerabilities in general~\cite{SZ12}.
The scope of that research is pretty wide and leaves
out many approaches and mechanisms that we report here.
This is mainly because this work includes countermeasures
that detect such vulnerabilities via program analysis
(which is done during development or testing), while
we include protection mechanisms that counter
such attacks when they take place.
Also, countermeasures that prevent {\sc sql}
injection attacks~\cite{HVO06}, have already been surveyed.
However, this survey is quite old and since then
the number of countermeasures that detect {\sc sql}
injection attacks alone, has been drastically increased
as we mentioned in the previous paragraph.

In our research we focus on the top
{\sc tba} systems that and are presented
in publications cited more than twenty times.
For the sake of our study, we choose
to make some exceptions and include some latest mechanisms
that were presented in top security conferences even if
the corresponding publications have been cited less than
twenty times.

% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.

Introduction~\cite{I05}. Also see~\cite{A00}.

Requirements:
\begin{itemize}
\item {\it Diagnostic Performance} As long
as we examine protection mechanisms that detect
attacks, the non-existence of false positive and
negative alarms is a reasonable requirement.
\item {\it Computational Performance} We examine
the overhead of the mechanisms
that affect the experience of a web user who actually
uses the protected application.
\item {\it Ease of use} We examine if the protection
mechanism is practical in terms of deployment
and can be easily adopted by security experts.
\item {\it Security} How resilient is the system to
attackers that know how it works and wants to circumvent it.
\item {\it Detection Locus}
\item {\it Availability}
\end{itemize}

All the aforementioned requirements are considered critical
when building security mechanisms that protect
applications~\cite{A01,A00}.

>>>>

  We then categorize and analyze the various defense mechanisms that
  have been developed. Our analysis is based on dimensions such as
  accuracy, performance, deployment and security. Especially notable
  is accuracy, as our findings show that there are
  many defense mechanisms that are tested in a poor manner.
  In addition, we observe that there are many protection mechanisms
  that can be bypassed by attackers that know how the mechanisms
  work. Finally, we see that researchers tend to not make
  their mechanisms available to the community.

@@

%Introduction~\cite{I05}. Also see~\cite{A00}.

@@

In this paper we initially show how the above attacks can be seen from
a {\it common perspective}. We achieve this by providing
an exploitation model that highlights the following fact:
the majority of the steps needed to perform application attacks
based on executable source code injection are
common.\footnote{Note that we leave out attacks that are based on
binary code injection (i.e. buffer
overflows --- see Section~\ref{sec:attacks}).}
This is validated by the fact that there are
protection mechanisms that can detect more than
one of these attacks. Then, we {\it categorize}
the top 34 protection mechanisms that detect such attacks and
are presented in publications cited more than twenty times.
For the sake of our study, we choose
to make some exceptions and include some of the
latest mechanisms that were presented in top security
conferences even if the corresponding publications have
been cited less than twenty times. Finally, we {\it analyze}
each mechanism based on the following dimensions:
\begin{itemize}
\item {\it Diagnostic Performance} As long
as we examine protection mechanisms that detect
attacks, the non-existence of false positive and
negative alarms is a reasonable requirement.
\item {\it Computational Performance} We examine
the overhead of the mechanisms
that affect the experience of a web user who actually
uses the protected application.
\item {\it Ease of use} We examine if the protection
mechanism is practical in terms of deployment
and can be easily adopted by security experts.
\item {\it Security} How resilient is the system to
attackers that know how it works and wants to circumvent it.
\item {\it Detection Locus}
\item {\it Availability}
\end{itemize}

\noindent
All the aforementioned requirements are considered critical
when building security mechanisms that protect
applications~\cite{A01,A00}. Based on this analysis
we can identify the advantages and disadvantages of the
various mechanisms and enumerate some of their common
characteristics. We can also draw useful conclusions
about the various categories and see how they compare
to each other. A worrying observation is that sometimes,
researchers test the diagnostic performance of their
mechanisms in a poor manner. This turns out as very
critical because some of these mechanisms can actually
be bypassed. In addition, researchers do
not make their mechanisms available to the community,
thus no one can either use their mechanism,
or replicate their experiments.

There is already a survey on mitigating software vulnerabilities
in general~\cite{SZ12}. The scope of that
research is pretty wide and leaves out the majority of the
approaches and mechanisms that we report here.
This is mainly because this work includes countermeasures
that detect such vulnerabilities via program analysis
(which is done during development or testing), while
we include protection mechanisms that counter
such attacks when they take place.
Also, countermeasures that prevent {\sc sql}
injection attacks~\cite{HVO06}, have already been surveyed.
However, this survey is quite old and since then
the number of countermeasures that detect {\sc sql}
injection attacks alone, has been drastically increased
as we mentioned in the previous paragraph.

The main contributions of this paper are the following:

\begin{enumerate}
\item We provide an exploitation model that puts
application attacks based on executable source code injection
under a common perspective.
\item We categorize and analyze previously proposed
defenses based on criteria that are considered critical
when building protection mechanisms.
\item We discuss some serious issues raised from our
findings. Such can be the main reasons why
the mechanisms are not adopted in practice.
\item We discuss what are the necessary criteria
for new mechanisms and how our work can help
researchers to design new countermeasures.
\end{enumerate}

The rest of the paper is organized as follows. {\sc tba}.

% In the last 15 years there are numerous mechanisms that have
% been developed to detect one or more of the attacks mentioned
% above. However, the majority of them are not used in practice.
% This is due to the following reasons:
% a) the mechanisms have not been extensively tested in terms
% of accuracy,
% b) are hard to deploy because they require many modifications
% either on the client-side, the server-side, or both,
% c) they add significant overhead, and
% d) can be bypassed by attackers that know how they work.
% The motivation behind this research is to systematize
% and analyze previously proposed protection mechanisms.
% In this way we can highlight the advantages
% and disadvantages of each mechanism, enlist them
% into different categories, and see how they compare to each other.
